\papertitle

### 2021-03-04 source_separation/paper/paper.tex
Added ConvTasNet description

			\subsubsection{TDCNN (use full name instead of abbreviation)}
			@Leo/Alejandro

>>>>

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcnn} (TDCNN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modelling sequential data, as series of dilateds convolutions are a good way to capture temporal patterns.\\

			The purpose of the model was initially to separate multiple speakers from a single-channel audio, and was thus trained on speech datasets. Because of its good performance at speech separation, a pre-trained version of the model based on the settings of the paper was added to the benchmark.
